Two applications of logic programming to Coq

### 2020-10-30 papers/types2020/main.tex
"ordered" example in pbt.tex
adding file for conclusion
some work on fig 1
after main merge
added some related and future work, suggestions for title, revisions to sec 4
title changed and temporary abstract added

\title{Interfacing logic programming and Coq} % Other suggestions?
\titlerunning{Interfacing logic programming and Coq}

@@

\begin{abstract}
We do stuff
\end{abstract}

@@

\section{Conclusion}

\bibliography{l}
\end{document}

@@

>>>>

\title{Two applications of logic programming to Coq} % Other suggestions?
% bit too general -- elpi-coq is such an interface -a,
% on the usefulness of logic programming in Coq
% two applications of logic programming to Coq
\titlerunning{Two applications of logic programming to Coq}

@@

\begin{abstract}
The \emph{foundational proof certificate} (FPC) framework is capable
of checking and elaborating a wide range of proof evidence and can easily
be implemented using the logic programming language \lP.
%
% The checking of a proof certificate in this higher-order logic
% programming language can yield a fully detailed, dependently
% typed $\lambda$-terms that can be checked by the Coq kernel.
%
We use the recently released Coq-Elpi plugin for Coq in which the Elpi
implementation of \lP can send and retrive information to and from the Coq kernel.
%
We provide two examples: first we implement a FPC-driven sequent calculus for a fragment of the Calculus of Inductive Constructions and we package it into a tactic to perform property-based testing of Inductive types corresponding to pure (higher-order) Horn programs. Secondly, we implement a proof checker for first-order LJF to demonstrate how  proof certificates
can be supplied by external (to Coq) provers and elaborated into the
fully detailed proof terms that can be checked by the Coq kernel.
\end{abstract}

@@

\input conc
\bibliography{l}
\appendix
\input app
\end{document}

@@

% LocalWords:  pbt elab conc Elpi LJF
